Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments

### 2018-07-31 articles/formalism/sections/introduction.tex
updated reference for CORE

The primary aim of the current CMB experiments is to make precise measurements of CMB polarization. While the $E$-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review),  ongoing and future CMB experiments aim to measure the $B$-modes of CMB polarization with unprecedented accuracy. The instruments are swiftly approaching the desired sensitivities to enable us to in principle measure $B$-mode signals with $r\gtrsim 0.001$ \cite{Spider, CLASS,Litebird, BICEP22015, 2016arXiv161002743A, 2017arXiv170602464A,Remazeilles2018}. However $B$-modes generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.  Precise modelling and subtraction of this large foreground contribution poses a major challenge for a robust unravelling of the minuscule $B$-mode signal.

>>>>

The primary aim of the current CMB experiments is to make precise measurements of CMB polarization. While the $E$-modes of polarization have been measured reasonably well by a number of experiments (\cite{2018RPPh...81d4901S} gives a recent review),  ongoing and future CMB experiments aim to measure the $B$-modes of CMB polarization with unprecedented accuracy. The instruments are swiftly approaching the desired sensitivities to enable us to in principle measure $B$-mode signals with $r\gtrsim 0.001$ \cite{Spider, CLASS,Litebird, BICEP22015, 2016arXiv161002743A, 2017arXiv170602464A,Delabrouille2017}. However $B$-modes generated by galactic foreground are expected to be a few orders of magnitude higher than $B$-mode amplitude measurable by these detectors.  Precise modelling and subtraction of this large foreground contribution poses a major challenge for a robust unravelling of the minuscule $B$-mode signal.
